\documentclass[5p,sort&compress]{elsarticle}	

\input{setup.tex}

\begin{document}
\begin{frontmatter}

  \title{TFE4575: Fabrication of 675 nm wavelength LEDs}
  %\title{bonustitle}

  \author[fysikk]{Brynjar Morka Mæhlum}
  \author[fysikk]{Thord Niri Gjesdahl Heggren}
  \address[fysikk]{Department of Physics, Norwegian University of Science and Technology, 7491 Trondheim, Norway.}

  \begin{abstract}

    \noindent Light emitting diodes (LED) are widely used light producing electrical components.
    Producing LEDs is a micro- and nanotechnological processes.
    In this report, a premade multi-layered semiconductor wafer is used to produce LEDs.
    The wafer have been processed by strategically using photolithography, deposition, and etching.
    The LED have been characterized using an optical microscope, a scanning electron microscope, a profilometer, an ellipsometer and a SourceMeter.
    The characterizations revealed that some process steps resulted in minor defects.
    However, measurements of the IV-characteristics of the LEDs have been performed, and it confirmed that the LEDs are working as diodes.
    With voltage at 1.7 V and current at 30 mA the LEDs emits red light, which is the around the target wavelength of 675 nm.
    % Producing the LEDs did not always go as planned, and some defects and artifacts were produced.

  \end{abstract}


\end{frontmatter}

{ % This changes links to purple instead of blue
\hypersetup{linkcolor=purple}

\tableofcontents

%%% dette gjenstår:
% conclusion
% fikse layout 

% abstract
% IV i diskusjon
% IV measurements
% IV i metode
% IV i resultater


%%%%%%%%%%%%%%%%%%% INTRODUCTION %%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{intro}
\input{chapters/introduction.tex}

%%%%%%%%%%%%%%%%%%% THEORY %%%%%%%%%%%%%%%%%%
\section{Theory}
\label{theory}
\input{chapters/theory.tex}

%%%%%%%%%%%%%%%%%%% METHODS %%%%%%%%%%%%%%%%%%
\section{Methods}
\label{methods}
\input{chapters/methods.tex}

%%%%%%%%%%%%%%%%%%% RESULTS %%%%%%%%%%%%%%%%%%
\section{Results}
\label{results}
\input{chapters/results.tex}

%%%%%%%%%%%%%%%%%%% DISCUSSION %%%%%%%%%%%%%%%%%%
\section{Discussion}
\label{discussion}
\input{chapters/discussion.tex}

%%%%%%%%%%%%%%%%%%% CONCLUSION %%%%%%%%%%%%%%%%%%
\section{Conclusion}
\label{conclusion}
\input{chapters/conclusion.tex}

%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%
}
\begingroup
\begin{center}
  \rule{2cm}{.4pt}
\end{center}
\makeatletter
\@beginparpenalty=10000
\makeatother
\bibliographystyle{unsrt} %unsrtnat
\bibliography{references}


\endgroup

\end{document}